# Simulation

We check how well our model recovers generating parameter values by simulating a dataset from Equation \@ref(joint) and then fitting these data to this model. We choose generating parameter values that induce stable or minimal growth, as it is easy over a 51 year time series to simulate runaway growth with an exponential growth model. For this reason, we set site effects to be quite small while allowing year effects, which could be offsetting, to be larger. We ask the following questions:

1. Does the model recover the parameters, including site and year effects and breeding productivity?
2. How well does the model recover latent abundance and population growth rate multipliers?
3. Are nest abundances and growth rates biased and if so is this pattern related to sparseness in the observed data? 

## Simulate data

```{r}
set.seed(5)
sigma_sim <- .15
sigma_site_sim <- .05
gamma_sim <- 0
nu_sim <- 5 ###
eta_sim <- rnorm(n_sites, 0, sigma_site_sim)
alpha_sim <- rbeta(nrow(abundance_chicks), a, b)
site_n <- model_data$site_n
season_n <- model_data$season_n
site_c <- model_data$site_c
season_c <- model_data$season_c
s <- model_data$s
# region <- model_data$region
# ccamlr <- model_data$ccamlr
sigma_n <- abundance_nests$sigma
sigma_c <- abundance_chicks$sigma
sigma_i <- abundance_initial$sigma
y_n_sim <- y_c_sim <- y_i_sim <- z_c_sim <- N_sim <- gl_a_sim <- gl_p_sim <- NA
zr_sim <-  NA ###
lz_sim <- array(NA, dim = c(n_sites, n_seasons))
l_a_sim <- l_p_sim <- lw_a_sim <- lw_p_sim <- array(NA, dim = c(n_sites, (n_seasons - 1)))

for (i in 1:n_sites) {
  lz_sim[i, s[i]] <- LaplacesDemon::rst(1, log(1000), .75, nu = 5)
  for (t in (s[i] + 1):n_seasons) {
    zr_sim[i] <- gamma_sim + eta_sim[i]
    lz_sim[i, t] <- LaplacesDemon::rst(1, lz_sim[i, (t - 1)] + zr_sim[i], sigma_sim, nu_sim)
  }
  for (t in 1:(s[i] - 1)) {
    zr_sim[i] <- gamma_sim + eta_sim[i]
    lz_sim[i, (s[i] - t)] <- LaplacesDemon::rst(1, lz_sim[i, (s[i] - t + 1)] - zr_sim[i], sigma_sim, nu_sim)
  }
}

for (i in 1:nrow(abundance_nests)) {
  y_n_sim[i] <- rnorm(1, lz_sim[site_n[i], season_n[i]], sd = sigma_n[i])
}
for (i in 1:nrow(abundance_chicks)) {
  N_sim[i] <- as.integer(2 * round(exp(lz_sim[site_c[i], season_c[i]])))
  z_c_sim[i] <- base::max(rbinom(1, N_sim[i], prob = alpha_sim[i]), 1)
  y_c_sim[i] <- rnorm(1, log(z_c_sim[i]), sd = sigma_c[i])
}
for (i in 1:nrow(abundance_initial)) {
  y_i_sim[i] <- rnorm(1, lz_sim[i, s[i]], sd = sigma_i[i])
}

for (i in 1:n_sites) {
  for (t in 2:n_seasons) {
    l_a_sim[i, t - 1] <- exp(lz_sim[i, t] - lz_sim[i, t - 1]) 
    l_p_sim[i, t - 1] <- exp(zr_sim[i])
    if (w[i, t] == 1 & w[i, t - 1] == 1) {
      lw_a_sim[i, t - 1] <- l_a_sim[i, t - 1] 
      lw_p_sim[i, t - 1] <- l_p_sim[i, t - 1] 
    } else {
      lw_a_sim[i, t - 1] <- 1
      lw_p_sim[i, t - 1] <- 1
    }
  }
}

for (i in 1:n_sites) {
  gl_a_sim[i] <- prod(lw_a_sim[i, ])^(1/(sum(w[i, 1:n_seasons]) - 1))
  gl_p_sim[i] <- prod(lw_p_sim[i, ])^(1/(sum(w[i, 1:n_seasons]) - 1))
}

# create the data list for the JAGS model
model_sim <- list(
  nests = nrow(abundance_nests),
  y_n = y_n_sim, 
  precision_n = abundance_nests$precision,
  site_n = abundance_nests$site,
  season_n = abundance_nests$season_relative,
  chicks = nrow(abundance_chicks),
  y_c = y_c_sim, 
  precision_c = abundance_chicks$precision,
  site_c = abundance_chicks$site,
  season_c = abundance_chicks$season_relative,
  y_i = y_i_sim,
  precision_i = abundance_initial$precision,
  n_sites = n_sites,
  n_seasons = n_seasons,
  # n_regions = n_regions,
  # n_ccamlr = n_ccamlr,  
  s = as.vector(SiteList$initial_season),
  # region = as.vector(SiteList$region),
  # ccamlr = as.vector(SiteList$ccamlr), 
  w = w,
  a = a,
  b = b)

save(model_sim, file = "_static/model_sim.rda")
```

## Model fitting

```{r}
random_inits <- function(model_data) {
  seed = runif(1, 1, 100000)
  gamma <- runif(1, -.025, .025)
  # sigma_region <- runif(1, .05, .1)
  sigma_site <- runif(1, .025, .05)
  # sigma_season <- runif(1, .05, .1)
  sigma <- runif(1, .05, .1)
  chicks <- model_sim$chicks
  n_sites <- model_sim$n_sites
  n_seasons <- model_sim$n_seasons
  # n_regions <- model_sim$n_regions
  s <- model_sim$s
  # region <- model_sim$region
  # ccamlr <- model_sim$ccamlr
  y_c <- model_sim$y_c
  y_i <- model_sim$y_i
  site_c <- model_sim$site_c
  season_c <- model_sim$season_c
  a <- model_sim$a
  b <- model_sim$b
  eta <- rnorm(n_sites, 0, sigma_site)
  alpha <- rbeta(chicks, a, b)
  nu <- runif(1, 1, 50)
  zr <- NA ###
  lz <- array(NA, dim = c(n_sites, n_seasons))
  #
  for (i in 1:n_sites) {
    lz[i, s[i]] <- mean(y_i[i], na.rm = TRUE)
    for (t in (s[i] + 1):n_seasons) {
      zr[i] <- gamma + eta[i]
      lz[i, t] <- LaplacesDemon::rst(1, lz[i, (t - 1)] + zr[i], sigma, nu)
    }
    for (t in 1:(s[i] - 1)) {
      zr[i] <- gamma + eta[i]
      lz[i, (s[i] - t)] <- LaplacesDemon::rst(1, lz[i, (s[i] - t + 1)] - zr[i], sigma, nu)
     }
  }

  z_c <- N <- NA
  for (i in 1:chicks) {
    if (lz[site_c[i], season_c[i]] < 0) lz[site_c[i], season_c[i]] <- 0
    N[i] <- 2 * round(exp(lz[site_c[i], season_c[i]]))
    z_c[i] <- base::max(rbinom(1, prob = alpha[i], N[i]), 1)
  }
  
  return(list(
    sigma = sigma,
    # sigma_region = sigma_region,
    sigma_site = sigma_site,
    # sigma_season = sigma_season,
    gamma = gamma,
    # beta = beta,
    eta = eta,
    nu = nu, ###
    # epsilon = epsilon,
    alpha = alpha,
    lz = lz,
    z_c = z_c,
    .RNG.name = "base::Mersenne-Twister",
    .RNG.seed = seed))
}

save(random_inits, file = "_static/random_inits.rda")
expect_error(random_inits(model_sim), NA)
```

```{r, eval = FALSE, echo = TRUE}
n.chains <- 6
n.adapt <- 3000
n.update <- 200000
n.iter <- 100000
thin <- 100
cl <- makeCluster(n.chains)
cvars <- c("model_sim", "n.adapt", "n.update", "n.iter", "thin", "params", "random_inits")
params <- c("gamma", "sigma", "sigma_site", "alpha", "eta", "z_c", "lz", "gl_a", "l_a", "y_i_new",
            "y_n_new", "y_c_new", "y_n_sqs", "y_n_sqs_new", 
            "y_i_sqs_new", "y_i_sqs", "y_c_sqs", "y_c_sqs_new", "nu")
parallel::clusterExport(cl, cvars)
out <- clusterEvalQ(cl, {
  library(rjags)
  inits <- random_inits(model_sim)
  jm = jags.model("_static/jags_model.jags", data = model_sim, n.chains = 1, n.adapt = n.adapt, 
    inits = inits)
  update(jm, n.iter = n.update)
  zm = coda.samples(jm, variable.names = params, n.iter = n.iter, thin = thin)
  return(as.mcmc(zm))
})
stopCluster(cl)
model_sim_rinits_output = mcmc.list(out)  
save(model_sim_rinits_output, file = "_static/model_sim_rinits_output.rda")
```

```{r, fig.align = "center", fig.width = 12, fig.height = 8, fig.cap = "Trace plots for average intrinsic rate of growth and model variances (reported as standard devations)"}
MCMCsummary(model_sim_rinits_output, params = c("gamma", "sigma", "sigma_site", "nu"), 
  HPD = TRUE, hpd_prob = .95, round = 3)
color_scheme_set("viridis")
bayesplot_theme_update(text = element_text(size = 14, family = "sans"))
mcmc_trace(model_sim_rinits_output, regex_pars = c("gamma", "sigma", "nu"))
```

## Posterior predictive checks

```{r}
params <- c("y_i_sqs", "y_i_sqs_new", "y_n_sqs", "y_n_sqs_new", "y_c_sqs", "y_c_sqs_new")
MCMCsummary(model_sim_rinits_output, params = params, n.eff = FALSE, round = 3)
```

```{r, fig.align = 'center', fig.width = 12, echo = FALSE}
rep_data <- MCMCvis::MCMCchains(model_sim_rinits_output, params = 'y_i_new')
tdata_i <- bayesplot::ppc_data(model_sim$y_i, rep_data)
rep_data <- MCMCvis::MCMCchains(model_sim_rinits_output, params = 'y_n_new')
tdata_n <- bayesplot::ppc_data(model_sim$y_n, rep_data)
rep_data <- MCMCvis::MCMCchains(model_sim_rinits_output, params = 'y_c_new')
tdata_c <- bayesplot::ppc_data(model_sim$y_c, rep_data)

ppc1 <- ggplot(tdata_i, aes_(x = ~value)) +
  stat_density(aes_(group = ~rep_id, color = "simulated data"), geom = "line", position = "identity", 
    size = 0.25, alpha = 0.1, trim = FALSE, bw = 'nrd0', adjust = 1, kernel = 'gaussian', n = 1024,
    data = function(x) dplyr::filter(x, !tdata_i$is_y)) +  
  stat_density(aes_(color = "y"), data = function(x) dplyr::filter(x, tdata_i$is_y), geom = "line", 
    position = "identity", lineend = "round", size = 0.5, trim = FALSE, bw = 'nrd0', adjust = 1, 
    kernel = 'gaussian', n = 1024) +
  scale_color_manual(values = c('firebrick3', 'black')) +
  theme_classic() +
  labs(title = "Initial Abundance Density Plot", x = "logged nest abundance") +
  theme(legend.position = "bottom")  

ppc2 <- ggplot(tdata_n, aes_(x = ~value)) +
  stat_density(aes_(group = ~rep_id, color = "simulated data"), geom = "line", position = "identity", 
    size = 0.25, alpha = 0.1, trim = FALSE, bw = 'nrd0', adjust = 1, kernel = 'gaussian', n = 1024,
    data = function(x) dplyr::filter(x, !tdata_n$is_y)) +  
  stat_density(aes_(color = "y"), data = function(x) dplyr::filter(x, tdata_n$is_y), geom = "line", 
    position = "identity", lineend = "round", size = 0.5, trim = FALSE, bw = 'nrd0', adjust = 1, 
    kernel = 'gaussian', n = 1024) +
  scale_color_manual(values = c('firebrick3', 'black')) +
  theme_classic() +
  labs(title = "Nest Abundance Density Plot", x = "logged nest abundance") +
  theme(legend.position = "bottom")  

ppc3 <- ggplot(tdata_c, aes_(x = ~value)) +
  stat_density(aes_(group = ~rep_id, color = "simulated data"), geom = "line", position = "identity", 
    size = 0.25, alpha = 0.1, trim = FALSE, bw = 'nrd0', adjust = 1, kernel = 'gaussian', n = 1024,
    data = function(x) dplyr::filter(x, !tdata_c$is_y)) +  
  stat_density(aes_(color = "y"), data = function(x) dplyr::filter(x, tdata_c$is_y), geom = "line", 
    position = "identity", lineend = "round", size = 0.5, trim = FALSE, bw = 'nrd0', adjust = 1, 
    kernel = 'gaussian', n = 1024) +
  scale_color_manual(values = c('firebrick3', 'black')) +
  theme_classic() +
  labs(title = "Chick Abundance Density Plot", x = "logged chick abundance") +
  theme(legend.position = "bottom")  

ppc1 + ppc2 + ppc3
```

## Posterior predictive loss

```{r}
y_i_new_mean <- MCMCsummary(model_sim_rinits_output, params = c("y_i_new"), n.eff = FALSE)[, 1]
y_i_new_sd <- MCMCsummary(model_sim_rinits_output, params = c("y_i_new"), n.eff = FALSE)[, 2]
dsel_i <- sum((model_sim$y_i - y_i_new_mean)^2) + sum(y_i_new_sd^2)
y_n_new_mean <- MCMCsummary(model_sim_rinits_output, params = c("y_n_new"), n.eff = FALSE)[, 1]
y_n_new_sd <- MCMCsummary(model_sim_rinits_output, params = c("y_n_new"), n.eff = FALSE)[, 2]
(dsel_n <- sum((model_sim$y_n - y_n_new_mean)^2) + sum(y_n_new_sd^2) + dsel_i)
y_c_new_mean <- MCMCsummary(model_sim_rinits_output, params = c("y_c_new"), n.eff = FALSE)[, 1]
y_c_new_sd <- MCMCsummary(model_sim_rinits_output, params = c("y_c_new"), n.eff = FALSE)[, 2]
(dsel_c <- sum((model_sim$y_c- y_c_new_mean)^2) + sum(y_c_new_sd^2))
save(dsel_i, dsel_n, dsel_c, file = "_static/ppl_sim.rda")
```

```{r, echo = FALSE, fig.align = "center", fig.height = 40, fig.width = 12, warning = FALSE, fig.cap = "Scaled nest posterior predictive loss by site and season."}
abundance_nests$dsel_n_sim <- (model_sim$y_n - y_n_new_mean)^2 + y_n_new_sd^2
abundance_initial$dsel_n_sim <- (model_sim$y_i - y_i_new_mean)^2 + y_i_new_sd^2
work1 <- rbind(
  abundance_nests %>% 
    dplyr::select(site, season_relative, dsel_n_sim),
  abundance_initial %>% 
    dplyr::select(site, season_relative, dsel_n_sim)) %>%
  mutate(dsel_n_sim_scaled = dsel_n_sim / base::max(dsel_n_sim)) %>%
  right_join(w_template, by = c("site", "season_relative")) %>%
  mutate(site_id_rev = factor(site_id, levels = rev(sort(unique(site_id))))) %>%
  dplyr::select(site_id, site_id_rev, season, dsel_n_sim_scaled) %>%
  arrange(site_id, season)
  
p1 <- ggplot(work1, aes(x = factor(season), y = factor(site_id_rev), fill = dsel_n_sim_scaled)) +
  geom_tile(color = "black", width = .8, height = .8, size = .3) +
  scale_fill_gradient(low = "yellow", high = "red", na.value = "white", name = "Scaled PPL") +
  labs(x = "", y = "") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), breaks = seq(1970, 2015, 5), 
    labels = c("1970", "1975", "1980", "1985", "1990", "1995", "2000", "2005", "2010", "2015"))  +
  theme_grey(base_size = 8) +      
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 8),
    axis.ticks = element_line(size = .6),
    plot.background = element_blank(),
    panel.background = element_blank(),
    panel.border=element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(2, "cm"))
p1
```

```{r, echo = FALSE, fig.align = "center", fig.height = 40, fig.width = 12, warning = FALSE, fig.cap = "Scaled chick posterior predictive loss by site and season."}
abundance_chicks$dsel_c_sim <- (model_sim$y_c - y_c_new_mean)^2 + y_c_new_sd^2
work2 <- abundance_chicks %>%
  dplyr::select(site, season_relative, dsel_c_sim) %>%
  mutate(dsel_c_sim_scaled = dsel_c_sim / base::max(dsel_c_sim)) %>%
  right_join(w_template, by = c("site", "season_relative")) %>%
  mutate(site_id_rev = factor(site_id, levels = rev(sort(unique(site_id))))) %>%
  dplyr::select(site_id, site_id_rev, season, dsel_c_sim_scaled) %>%
  arrange(site_id, season)
  
p2 <- ggplot(work2, aes(x = factor(season), y = factor(site_id_rev), fill = dsel_c_sim_scaled)) +
  geom_tile(color = "black", width = .8, height = .8, size = .3) +
  scale_fill_gradient(low = "yellow", high = "red", na.value = "white", name = "Scaled PPL") +
  labs(x = "", y = "") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), breaks = seq(1970, 2015, 5), 
    labels = c("1970", "1975", "1980", "1985", "1990", "1995", "2000", "2005", "2010", "2015"))  +
  theme_grey(base_size = 8) +      
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 8),
    axis.ticks = element_line(size = .6),
    plot.background = element_blank(),
    panel.background = element_blank(),
    panel.border=element_blank(),
    legend.position = "bottom",
    legend.key.width = unit(2, "cm"))
p2
```

## Parameter recovery

```{r, echo = FALSE}
r_threshold <- 1.05
z_c_q <- MCMCsummary(model_sim_rinits_output, params = c("z_c"), HPD = TRUE, hpd_prob = .95, round = 3)[,c(3, 4, 5, 6)]
z_c <- cbind(data.frame(z_c_q), abundance_chicks, z_c_sim) %>%
  mutate(no_recovered = ifelse(z_c_sim >= X95._HPDL & z_c_sim <= X95._HPDU, 0, 1)) %>%
  mutate(no_converged = ifelse(Rhat <= r_threshold | is.na(Rhat), 0, 1)) %>%
  dplyr::select(site_id, site_id, season, no_recovered, no_converged) %>%
  summarise(no_recovered = sum(no_recovered), no_converged = sum(no_converged))

alpha_q <- MCMCsummary(model_sim_rinits_output, params = c("alpha"), HPD = TRUE, hpd_prob = .95, round = 3)[,c(3, 4, 5, 6)]
alpha <- cbind(data.frame(alpha_q), abundance_chicks, alpha_sim) %>%
  mutate(no_recovered = ifelse(alpha_sim >= X95._HPDL & alpha_sim <= X95._HPDU, 0, 1)) %>%
  mutate(no_converged = ifelse(Rhat <= r_threshold | is.na(Rhat), 0, 1)) %>%
  dplyr::select(site_id, site_id, season, no_recovered, no_converged) %>%
  summarise(no_recovered = sum(no_recovered), no_converged = sum(no_converged))
```

The model performs well with simulation, recovering almost all parameters. Of the `r dim(z_c_q)[1]` latent chick abundances and breeding productivity parameters, `r z_c$no_converged` abundance and `r alpha$no_converged` breeding productivity parameters failed to converge and we did not recover `r z_c$no_recovered` chick abundance and `r alpha$no_recovered` breeding productivity generating values. We visualize additional parameters more fully below. The model sometimes consistently overestimates or underestimates latent abundances ina few time series. Despite this failure, the model does better at recovering seasonal and average site population growth rate multipliers.

```{r, fig.align = "center", fig.height = 40, fig.width = 12, echo = FALSE, warning = FALSE, fig.cap = "Recovery and convergence of latent nest abundance estimates across all sites and seasons. Green (yellow) filled boxes indicate abundance the generating value was above (below) the 95% highest posterior density credible (HPDC) interval, while gray boxes indicate the generating value was within the HPDC interval. Border color indicates the type of count observed for that site and season with purple being nest only, orange being chick only, and red being both nest and chick. Black dots mark abundance estimates that failed to converge."}

lz_sim_df <- data.frame(lz_sim) %>% 
  pivot_longer(cols = starts_with('X'), names_to = 'X', values_to = 'lz_sim')
lz_q <- data.frame(MCMCsummary(model_sim_rinits_output, params = c("lz"), HPD = TRUE, hpd_prob = .95, 
  round = 3, n.eff = FALSE))[, c(3, 4, 5)]
work3 <- cbind(lz_q, w_template) %>%
  mutate(season = season_relative + min_season - 1) %>%
  arrange(site, season_relative) %>%
  mutate(lz_sim = lz_sim_df$lz_sim) %>%
  mutate(recover = case_when(
    lz_sim < X95._HPDL ~ 1, 
    lz_sim > X95._HPDU ~ 2,
    lz_sim >= X95._HPDL & lz_sim <= X95._HPDU ~ 3)) %>%
  mutate(converged = ifelse(Rhat <= r_threshold, NA, 4)) %>%
  left_join(abundance_viz, by = c("site_id", "season")) %>%
  mutate(site_id_rev = factor(site_id, levels = rev(sort(unique(site_id))))) %>%
  dplyr::select(site_id, site_id_rev, season, recover, converged, type)

p3 <- ggplot(work3, aes(x = factor(season), y = factor(site_id_rev), fill = as.factor(recover))) +
  geom_tile(aes(color = as.factor(type), width = .8, height = .8), size = .75)  +
  scale_fill_manual(values = alpha(c("yellow", "green", "gray"), .3), na.value = NA) +
  scale_colour_manual(values = c("purple", "orange", "red", "black"), na.value = NA) +
  geom_point(aes(color = as.factor(converged)), size = 1) +
  labs(x = "", y = "") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), breaks = seq(1970, 2025, 5), 
    labels = c("1970", "1975", "1980", "1985", "1990", "1995", "2000", "2005", "2010", "2015", "2020", "2025"))  +
  theme_grey(base_size = 8) +      
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 8),
    axis.ticks = element_line(size = .6),
    plot.background = element_blank(),
    panel.background = element_blank(),
    panel.border=element_blank(),
    legend.position = "none")
p3
```

<br>

```{r, fig.align = "center", fig.height = 40, fig.width = 12, echo = FALSE, eval = TRUE, warning = FALSE, fig.cap = "Recovery and convergence of latent population growth rate multipliers across all sites and seasons. Green (yellow) filled boxes indicate abundance the generating value was above (below) the 95% highest posterior density credible (HPDC) interval, while gray boxes indicate the generating value was within the HPDC interval. Border color indicates the type of count observed for that site and season with purple being nest only, orange being chick only, and red being both nest and chick. Black dots mark population growth rate multipliers that failed to converge."}

l_a_sim_df <- data.frame(l_a_sim) %>% 
  pivot_longer(cols = starts_with('X'), names_to = 'X', values_to = 'l_a_sim')
l_a_q <- data.frame(MCMCsummary(model_sim_rinits_output, params = c("l_a"), HPD = TRUE, hpd_prob = .95, 
  round = 3, n.eff = FALSE))[, c(3, 4, 5)]
work4 <- cbind(l_a_q, w_template %>% 
  dplyr::filter(season_relative < n_seasons)) %>%
  mutate(season = season_relative + min_season - 1) %>%
  arrange(site, season_relative) %>%
  mutate(l_a_sim = l_a_sim_df$l_a_sim) %>%
  mutate(recover = case_when(
    l_a_sim < X95._HPDL ~ 1, 
    l_a_sim > X95._HPDU ~ 2,
    l_a_sim >= X95._HPDL & l_a_sim <= X95._HPDU ~ 3)) %>%
  mutate(converged = ifelse(Rhat <= r_threshold, NA, 4)) %>%
  left_join(abundance_viz, by = c("site_id", "season")) %>%
  mutate(site_id_rev = factor(site_id, levels = rev(sort(unique(site_id))))) %>%
  dplyr::select(site_id, site_id_rev, season, recover, converged, type)

p4 <- ggplot(work4, aes(x = factor(season), y = factor(site_id_rev), fill = as.factor(recover))) +
  geom_tile(aes(color = as.factor(type), width = .8, height = .8), size = .75)  +
  scale_fill_manual(values = alpha(c("yellow", "green", "gray"), .3), na.value = NA) +
  scale_colour_manual(values = c("purple", "orange", "red", "black"), na.value = NA) +
  geom_point(aes(color = as.factor(converged)), size = 1) +
  labs(x = "", y = "") +
  scale_y_discrete(expand = c(0, 0)) +
  scale_x_discrete(expand = c(0, 0), breaks = seq(1970, 2025, 5), 
    labels = c("1970", "1975", "1980", "1985", "1990", "1995", "2000", "2005", "2010", "2015", "2020", "2025"))  +
  theme_grey(base_size = 8) +      
  theme(
    axis.text.x = element_text(size = 10),
    axis.text.y = element_text(size = 8),
    axis.ticks = element_line(size = .6),
    plot.background = element_blank(),
    panel.background = element_blank(),
    panel.border=element_blank(),
    legend.position = "none")
p4
```

```{r, fig.align = "center", echo = FALSE, fig.cap = "Equal tailed credible intervals of the posterior distributions for average intrinsic rate of growth and model variances (reported as standard devations). Thin (thick) lines represent 95% (50%) credible intervals and points represent posterior medians. Red dots indicate generating values from the simulation."}
MCMCplot(model_sim_rinits_output, params = c("gamma", "sigma", "nu"), ISB = FALSE, horiz = TRUE, guide_lines = TRUE)
points(c(gamma_sim, sigma_sim, sigma_site_sim, nu_sim), seq(4, 1), col = "red", pch = 16)
```

```{r, fig.align = "center", fig.height = 40, echo = FALSE, fig.cap = "Equal tailed credible intervals of the posterior distributions for site effects (deviations from the average intrinsic rate of growth). Thin (thick) lines represent 95% (50%) credible intervals and points represent posterior medians. Red dots indicate generating values from the simulation."}
MCMCplot(model_sim_rinits_output, params = "eta", horiz = TRUE, labels = SiteList$site_id, sz_labels = .6, 
  guide_lines = TRUE, xlim = c(-.2, .2))
points(eta_sim, n_sites:1, col = "red", pch = 16)
```

```{r, fig.align = "center", fig.height = 40, echo = FALSE, fig.cap = "Equal tailed credible intervals of the posterior distributions for site-level average population growth rate multipliers. Thin (thick) lines represent 95% (50%) credible intervals and points represent posterior medians. Red dots indicate generating values from the simulation."}
MCMCplot(model_sim_rinits_output, params = "gl_a", horiz = TRUE, labels = SiteList$site_id, sz_labels = .6, 
  guide_lines = TRUE, ref = 1)
points(gl_a_sim, n_sites:1, col = "red", pch = 16)
```
